Forschungsprojekt

### 2020-10-20 documentation/presentation/main.tex
conclusion
Seitenzahlen
Folienreihenfolge geändert
Frameworks Folie wieder normal breit

@@

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=2cm, right=2cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Frameworks}
\vfill
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccp{8cm}p{6cm}}
	Framework&Version&NUMA&Dist.&\multicolumn{1}{c}{Features}&\multicolumn{1}{c}{Notes}\\
	\toprule
	$\color{Galois}\blacksquare$\ \bf Galois&29.06.2020&\checkmark&(\checkmark)&general purpose library designed for parallel programming, Hugepage support&distributed using Gluon\\\midrule
	$\color{Gemini}\blacksquare$\ \bf Gemini&02.11.2016&\checkmark&\checkmark&distributed message-based approach from scratch&version contains bugs that had to be fixed \\\midrule
	$\color{Giraph}\blacksquare$\ \bf Giraph&08.05.2020&X&\checkmark&built on Apache Hadoop&BFS is not natively supported \\\midrule
	$\color{Ligra}\blacksquare$\ \bf Ligra&14.08.2019&\checkmark&X&dynamically switches between push and pull style&\\\midrule
	$\color{Polymer}\blacksquare$\ \bf Polymer&28.08.2018&\checkmark&X&optimizes data layout and memory access strategies&\\
\end{tabular}
\vfill

@@

2) single node almost always preferrable, as long as RAM is sufficient
\begin{multicols}{2}
	\subsection{Production Case}
	\begin{itemize}
		\item Giraph is very fast on distributed systems (especially SSSP and BFS)
		\item Gemini and Ligra are good options for single node
	\end{itemize}

>>>>

\rfoot{\makebox[\textwidth][r]{\sffamily\thepage}}

@@

%\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=2cm, right=2cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Frameworks}
\vfill
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccp{7cm}p{5cm}}
	Framework&Version&NUMA&Dist.&\multicolumn{1}{c}{Features}&\multicolumn{1}{c}{Notes}\\
	\toprule
	$\color{Galois}\blacksquare$\ \bf Galois&29.06.2020&\checkmark&(\checkmark)&general purpose library designed for parallel programming, Hugepage support&distributed using Gluon\\\midrule
	$\color{Gemini}\blacksquare$\ \bf Gemini&02.11.2016&\checkmark&\checkmark&distributed message-based approach from scratch&version contains bugs that had to be fixed \\\midrule
	$\color{Giraph}\blacksquare$\ \bf Giraph&08.05.2020&X&\checkmark&built on Apache Hadoop&BFS is not natively supported \\\midrule
	$\color{Ligra}\blacksquare$\ \bf Ligra&14.08.2019&\checkmark&X&dynamically switches between push and pull style&\\\midrule
	$\color{Polymer}\blacksquare$\ \bf Polymer&28.08.2018&\checkmark&X&optimizes data layout and memory access strategies&\\
\end{tabular}
\vfill

@@

2) single node almost always preferrable, as long as RAM is sufficient
\begin{multicols}{2}
	\subsection{Production Case}
	\begin{itemize}
		\item Giraph is very fast on distributed systems (especially SSSP and BFS)
		\item Gemini is fast for distributed PR
		\item Gemini and Ligra are good options for single node
	\end{itemize}
